PhD Research Proposal: Molecular Level Design of Nanoporous Lyotropic Liquid Crystal Membranes for Aqueous Separations \\ \vspace{0.5cm} \large Advisors: Michael Shirts and Richard Noble

### 2019-05-16 Ben_Manuscripts/comps/Draft.tex
Updates to draft and new figures

%MRS: overall, really nice start.  You can cut back a little on the detail and emphasize a bit more ``This is what the data means and what the consequnces are.  Need to flesh out objective 3 a more (and objective 4 a bit more). 
\author{Benjamin J. Coscia}

@@

  More highly selective nanoporous membranes would be useful for 
  performing complex aqueous separations with seawater and various
  types of wastewater. For example, sodium chloride and boron in seawater 
  \cite{fritzmann_state---art_2007} and organic micropollutants found in
  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
  represent a small subset of the diverse contaminants of water sources. 
  By efficiently separating contaminants from feed solutions with
  highly selective membranes, it is possible to reduce the number of 
  required membrane passes and post-treatment steps needed for a given 
  filtration process \cite{werber_materials_2016}, thus lowering energy 
  requirements and cost. Additionally, one can extract valuable 
  resources from the feed streams. For example, flowback water produced 
  during hydraulic fracturing of shale formations contains dissolved 
  species like acetate whose extraction has economic value \cite{dischinger_application_2017}.

@@

  The downfall of RO and NF membranes can be summarized by the well-known
  permeability-selectivity tradeoff. Namely, it is difficult to increase the
  permeability of a desired molecular or atomic species, while maintaining
  the same retention of an undesired species.\cite{werber_materials_2016}

@@

  Nanostructured membranes attempt to overcome the permeability-selectivity 
  tradeoff through intelligent design at the molecular level. Graphene sheets, 
  carbon nanotubes (CNTs) and zeolites are three highly studied nanostructured
  technologies.

  Ultrathin-film graphene and graphene oxide membranes are a very active
  area of research because they offer potential for extremely high 
  permeability membranes. An ideal graphene membrane is a 2D material 
  composed of a single layer of graphene.\cite{humplik_nanostructured_2011}
  Synthesis of a single layer of graphene at a large scale without introducing
  defects is a challenge that has not yet been overcome. Multilayered graphene
  membranes are potentially easier to synthesize and more scalable which has 
  resulted in an increasing interest over recent years.\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}

  Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001} 
  Practically, dispersing CNTs into a polymer matrix is extremely difficult
  because they tend to agglomerate due to Van der Waals forces. Functionalization
  of the CNT walls has been heavily investigated  as a way to overcome this issue, however 
  alignment of the CNTs into an array feasible as a nanoporous membrane 
  persists as a challenge to CNT membranes.\cite{sahoo_polymer_2010}

  Zeolite-coated ceramic membranes offer the potential for permeabilities
  comparable to ultrafiltration, molecular sieves with pores up to 100 nm in 
  size~\cite{werber_materials_2016}, with selectivities as good as NF and RO. 
  Zeolites have highly uniform nm-sized crystalline structures with cage-like
  cavities that allow movement and trapping of small solutes. The crystalline
  frameworks are typically formed by networks of silicon and aluminum each 
  attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
  One can replace the silicon and aluminum atoms via ion exchange in order to
  control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}
  A number of studies have tested the permeability and sodium salt rejection
  of various zeolite membranes, however none have fully overcome the 
  permeability-selectivity tradeoff.~\cite{pendergast_review_2011}
%    \item Most are prone to defects in the crystalline structure.

@@

  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
  (LLC) membranes can be produced at moderate scale and may be capable of 
  performing highly selective separations. LLCs are amphiphilic molecules 
  that have the ability to self-assemble into porous nanostructures~\cite{smith_ordered_1997}
  that can be cross-linked to create mechanically strong membrane films with 
  periodic uniform-sized pores on the order of 1 nm in diameter~\cite{zhou_supported_2005}. 
  Since LLC polymer membranes lack an appreciable pore size distribution, they 
  inherently exhibit high selectivity due to their molecular weight cut-off 
  (MWCO)~\cite{zhou_supported_2005}. Additionally, LLC monomers can be salts,
  and therefore lead to Donnan exclusion of ions at the membrane-feed solution 
  interface.\cite{donnan_theory_1995}
%    The membrane gains a net surface charge when counterions from
%  the head groups that line the pore walls escape into the feed solution in an
%  effort to balance the gradients of concentration and electric potential
%  \cite{donnan_theory_1995}.

  % BJC: should show figure with HII and QI monomer structures
  The feasibility of nanostructured LLC polymer membranes for selective separations
  has been demonstrated using LLC monomers that form the type 1 bicontinuous cubic
  (Q\textsubscript{I})~\cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
  and the inverted hexagonal (H\textsubscript{II}) 
  phases (see Figure~\ref{fig:structures}).~\cite{zhou_supported_2005} When separating organic solutes from NaCl, Q\textsubscript{I}-phase
  membrane filtration experiments have shown selectivity 2--3 times higher than
  commercial RO and 6--12 times higher than commercial NF membranes.~\cite{dischinger_application_2017}
  When separating a series of various sized dyes, an H\textsubscript{II}-phase 
  LLC membrane showed complete rejection of dyes bigger than 1.2 nm in size~\cite{zhou_supported_2005}.

@@

  \noindent There are four primary objectives of this PhD research.
  \begin{enumerate}

    \item Develop techniques to build and understand the nanoscopic structure
    of LLC membranes.

    %MRS: probably should talk about this 1) with proper tense (some of these things have been done) and 2) talk about what YOU are doing, not we. I helped design the research, but you carried essentially all of it out! If phrased in future tense, committee will be confused, thinking those are things still to be done.

    A useful molecular-level model should incorporate a detailed picture 
    of the nanoscopic pore structure, which is crucial to understanding
    the role of monomer structure in solute transport and membrane design.
    I have created a maximally consistent structural model by comparing 
    simulated X-ray diffraction (XRD) patterns, generated from MD trajectories,
    to an experimental 2D wide angle X-ray scattering (WAXS) spectrum of a 
    Col\textsubscript{h} phase LLC membrane. I have used this model as an 
    example in order to understand the ease with which we can apply our approach
    to alternate monomers and other LC phases.

@@

    \item Determine dominant solute-membrane interactions that give rise to
    transport mechanisms.

    I observed the transport of a relatively large set of small polar solutes
    placed within the H\textsubscript{II} phase membrane nanopores. I analyzed
    the time series of each solute's position in addition to directly measuring
    the physical interactions, such as hydrogen bonding and ion coordination, 
    between solutes and LLC monomers.

    \item Create a stochastic model which can project long timescale 
    transport behavior.

@@

    \item Adapt the same analysis to the Q\textsubscript{I} phase.

@@

%MRS: overall, good description of wha has been done.  You can cut back a little if space is an issue.  Give the paper citations with the points. 
  \section{Progress to Date}\label{section:progress}

@@

  My first task was to develop a procedure for building and equilibrating 
  an atomistic LLC membrane system (see Figure~\ref{fig:assembly}). I chose to build
  a monoclinic unit cell consisting of four pores. Each pore is composed of monomer
  columns, where each column consists of 20 monomers stacked on top of each other
  so that the phenyl groups are coplanar with each other and the $xy$ plane. The
  columns are oriented so that the hydrophilic monomer head groups face towards
  the pore center. I did not add any water to the initial configuration because I
  compared the structure to experimental data for a system claimed to be
  synthesized with only neat monomer. I equilibrated unit cells using a series
  of simulations with head groups held in place by position restraints, gradually
  reducing the force constant of the position restraints until the system
  was completely unrestrained. I let the system equilibrate for 400 ns of simulation
  time.

@@

  I evaluated a number of different initial column architectures. I stacked 
  monomers in parallel displaced and sandwiched configurations, two possible
  $\pi$-$\pi$ stacking modes.\cite{sinnokrot_estimates_2002} I also varied 
  the initial distance between stacked monomers, $d$. I chose $d$ values of 
  3.7~\AA, based on experimental WAXS measurements, as well as 5 \AA~as a 
  test of its sensitivity.

@@

  \begin{wrapfigure}{L!}{0.5\textwidth}
    \centering
    \vspace{-0.5cm}
    \includegraphics[width=\linewidth]{p2p.pdf}
    \caption{Systems with 5 columns per pore have equilibrated pore spacings
            closest to the experimental value of 4.12 nm. The equilibrated 
            pore spacing of the model increases as the number of columns in
            each pore increases.}~\label{fig:p2p}
    \vspace{-1.75cm}
  \end{wrapfigure}

@@

  I further validated the structure of our molecular model by verifying 
  its consistency with five major reflections present in the experimental
  WAXS pattern. Using MD trajectories, we simulated X-ray diffraction (XRD)
  patterns that we could compare to the WAXS data by taking the appropriate
  cross-section of the time-averaged 3D structure factor. The five major 
  reflections and the structural features leading to them are summarized
  and described in the caption of Figure~\ref{fig:WAXS_comparison}. None of
  the models simulated to this point could reproduce R-double.

  It is necessary to add a small amount of water to the model in order to 
  fully reproduce all features of the WAXS pattern (see Figure~\ref{fig:solvated_XRD}).
  I obtain the most experimentally consistent structure when I build systems
  in the parallel displaced configuration with 1 wt\% water added to the pores. 
  This is the only configuration that gives rise to the R-double feature. R-double
  appears because vertically adjacent monomer head groups hydrogen bond with shared 
  water molecules, causing them to be drawn closer together. When multiple 
  pairing interactions occur in series along the same pore axis, the center
  of masses of the pairs are spaced apart at twice the $\pi$-stacking distance. 
  The necessity of water in my model suggests that the membrane synthesized by
  Feng et al. was slightly hydrated due to water molecules leached from 
  surroundings by the hydroscopic monomers. Similar suspicions have been voiced
  by experimentalists in unpublished communications.

  \begin{wrapfigure}{R!}{0.65\textwidth}
  	\centering
  	\vspace{-0.5cm}
    \begin{subfigure}{0.49\linewidth}
    	\includegraphics[width=\linewidth]{WAXS_annotated_words.pdf}
        \caption{Experiment}\label{fig:WAXS}
    \end{subfigure}
	\begin{subfigure}{0.49\linewidth}
        \includegraphics[width=\linewidth]{solvated_offset_rzplot_1.pdf}
        \caption{Simulation}\label{fig:solvated_XRD}   
	\end{subfigure}
    \caption{(a) 2D-WAXS gives details about repeating features on the order of
    angstroms. Explanations for each of the 5 major reflections present are
    as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack 3.7 \AA~apart. 
    (R-double) Monomer head groups associate into pairs by hydrogen bonding with
    a shared water molecule. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. 
    (R-spots) Monomer tails pack hexagonally. (R-pores) The pores are spaced 
    4.12 nm apart and pack hexagonally. (b) We obtain a maximally consistent
    match between simulated XRD patterns and experimental WAXS data when we
    build systems in the parallel displaced configuration with 1 wt \% water
    included in the pores.}\label{fig:WAXS_comparison}
    \vspace{-0.75cm}
 \end{wrapfigure}

  %BJC: I think this is important to say somewhere
  %BJC: but I don't have an ensemble of 1 wt % systems to fully prove that with.
  %BJC: I could show cross-sections of R-pi, but that would require more context. 
  On the timescales that we can reasonably simulate, our model exhibits slow 
  dynamics. Consequently, there are very few uncorrelated frames in our 
  trajectories which leads to noise and sharpened reflections in the simulated
  XRD patterns. We can overcome this issue by combining the structure factors
  generated from an ensemble of trajectories produced starting from an ensemble
  of uncorrelated initial configurations.

  The composition of the pores does not change regardless of which
  initial configuration we study. In Figure~\ref{fig:overlaid_densities}, we 
  plot the radial density of various monomer components as a function of distance
  from the pore centers. All are qualitatively similar meaning that a solute 
  placed in any of these systems should experience a similar chemical environment.
  Although we will move forward with our most promising configuration, this is 
  an important finding since it implies that we do not need to apply the same level
  of rigor when screening new monomers.

  My work towards this objective is published in the Journal of Physical Chemistry B:
  Coscia et al. \textit{J. Phys. Chem. B}, 123, 289-309 (2019).

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  %BJC: probably change this legend to `d = x Angstroms` instead of 
  % disordered/ordered, since I don't have space to talk about ordered / disorderd configurations (requires 
  % nematic order parameter to give a complete justification of the names)
  \includegraphics[width=\textwidth]{regional_density_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.pdf}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.pdf}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.pdf}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  \caption{In all systems studied, the component radial distribution functions are similar.
      They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
          regions. The biggest differences are at r=0 where noise is higher due to
          decreased sampling. The center of the pore is not hollow, but contains sodium ions and
          head groups, even when the system is solvated. This architecture may impede transport in
          the real system in a chemically-dependent manner.
          The solvated system has a lower density of head groups near the
          pore center which is likely due to the swelling that is necessary in order to fit water
          molecules in the pore region.}~\label{fig:overlaid_densities}
  \vspace{-0.5cm}
  \end{figure}

@@

  We added additional water to our most experimentally consistent structural
  model in order to create a higher water content H\textsubscript{II} phase
  model. Researchers have synthesized the H\textsubscript{II} phase using 
  the NaGA3C11 monomer with water contents ranging from 7 - 20 wt\%, with 
  10 wt\% being the most common.~\cite{smith_ordered_1997,zhou_supported_2005} 
  However, Resel et al. stated that the system is likely fully hydrated at
  7 wt \% water with additional water trapped in defects between mesophases.~\cite{resel_structural_2000}
  Consequently, we chose to build two systems with 5 and 10 wt\% water.

  \begin{wrapfigure}{l}{0.65\textwidth}
  \centering
  \vspace{-0.4cm}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{component_density_dry.pdf}
%  %BJC: simulation is extended to smooth out these curves
%  \caption{Dry System}\label{fig:component_density_dry}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \vspace{-0.5cm}
%  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
%  \label{fig:monomer_color_coded}
%  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to
  the color-coded monomer pictured in Figure~\ref{fig:HII_mon}. All RDFs
  represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin to which they belong. The black
  dashed lines are positioned so that they intersect with the maximum head group
  density. (a) In the 5 wt \% system, monomer head groups are situated about 0.45 nm
  from the pore center. Sodium and water are densest near the pore center 
  (b) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
  for more water. Water is densest at the pore center, but sodium ion density
  peaks closer to the head groups since many stay bound to carboxylate groups.}\label{fig:component_densities}
  \vspace{-0.75cm}
  \end{wrapfigure}

@@

  % BJC: do you think I can get away with an appendix with the solute table + abbreviations that
  % doesn't count towards the page limit?
  We observed transport of 20 different small polar solutes in the pores of
  our model. We created a separate initial configuration for each solute 
  studied and placed 6 solutes, equally spaced in $z$, in each nanopore.
  After a 5 ns equilibration, we allowed the solutes to simulate for
  1 microsecond.

>>>>

\author{Benjamin J. Coscia}

@@

    %MRS2: rephrase; sound like you are talking about only a minor problem. I would suggest adding a few more with citations
  %MRS2: to show you are aware of the breadth of the subject, and these aren't the only ones you know about.
  %represent a small subset
  %BJC2: rephrased then added 4 more citations

  More highly selective nanoporous membranes would be useful for 
  performing complex aqueous separations with seawater and various
  types of wastewater. For example, separating sodium chloride and 
  boron in seawater could yield potable drinking water in water scarce
  regions~\cite{fritzmann_state---art_2007} while separation of organic
  micropollutants found in municipal and industrial wastewaters could 
  make existing water supplies safer to drink~\cite{schwarzenbach_challenge_2006}.
  These represent only a few of the diverse contaminants of water sources~\cite{singh_production_2009,liu_removal_2008}. 
  By efficiently separating contaminants from feed solutions with
  highly selective membranes, it is possible to reduce the number of 
  required membrane passes and post-treatment steps needed for a given 
  filtration process \cite{werber_materials_2016}, thus lowering energy 
  requirements and cost. Additionally, one can extract valuable 
  resources from the feed streams~\cite{sales_resource_2015}. For example,
  flowback water produced during hydraulic fracturing of shale 
  formations contains dissolved species like acetate whose extraction has 
  economic value \cite{dischinger_application_2017,theodori_hydraulic_2014}.

@@

  The downfall of RO and NF membranes can be summarized by the well-known
  permeability-selectivity tradeoff. Namely, it is difficult to increase the
  permeability of a desired molecular or atomic species, while maintaining
  the same retention of undesired species.\cite{werber_materials_2016}

@@

  % BJC2: condensed this section into one paragraph
  Nanostructured membranes attempt to overcome the permeability-selectivity 
  tradeoff through intelligent design at the molecular level. 
%  Graphene sheets, carbon nanotubes (CNTs) and zeolites are three highly
%  studied nanostructured technologies. 
  Ultrathin-film graphene and graphene oxide membranes are an active area
  of research because they are atomically thick and therefore offer potential
  for extremely high permeability membranes.~\cite{humplik_nanostructured_2011}
  However, scalable synthesis without introducing microscopic, performance
  degrading defects has not yet been achieved.~\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
  Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001} 
  Practically, dispersing and aligning CNTs into a polymer matrix is extremely
  difficult because they tend to agglomerate due to Van der Waals forces.~\cite{sahoo_polymer_2010}
  Finally, zeolite-coated ceramic membranes offer the potential for permeabilities
  comparable to ultrafiltration, molecular sieves with pores up to 100 nm in 
  size~\cite{werber_materials_2016}, with selectivities as good as NF and RO. 
  A number of studies have tested the permeability and sodium salt rejection
  of various zeolite membranes, however none have fully overcome the 
  permeability-selectivity tradeoff.~\cite{pendergast_review_2011,auerbach_handbook_2003,li_novel_2007}

  %MRS2: this section is not so useful, becaue it talks about things you are NOT doing.  In a dissertation, would be good 
  %MRS2: context, but here, it distracts a bit because it's not summarizing what you are presenting in this paper. i.e. with 15 pages, you don't want to spend space talking about what you aren't doing.  Ideally, cut down to 1 paragraph just to
  %MRS2: show that you are aware of existing technologies.
  %BJC2: condensed above
%  Ultrathin-film graphene and graphene oxide membranes are a very active
%  area of research because they offer potential for extremely high 
%  permeability membranes. An ideal graphene membrane is a 2D material 
%  composed of a single layer of graphene.\cite{humplik_nanostructured_2011}
%  Synthesis of a single layer of graphene at a large scale without introducing
%  defects is a challenge that has not yet been overcome. Multilayered graphene
%  membranes are potentially easier to synthesize and more scalable which has 
%  resulted in an increasing interest over recent years.\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}
%  
%  Carbon nanotubes (CNTs) have shown promise as aqueous separations membranes
%  due to unprecedentedly fast water transport.\cite{humplik_nanostructured_2011,hummer_water_2001} 
%  Practically, dispersing CNTs into a polymer matrix is extremely difficult
%  because they tend to agglomerate due to Van der Waals forces. Functionalization
%  of the CNT walls has been heavily investigated  as a way to overcome this issue, however 
%  alignment of the CNTs into an array feasible as a nanoporous membrane 
%  persists as a challenge to CNT membranes.\cite{sahoo_polymer_2010}
%   
%  
%  Zeolites have highly uniform nm-sized crystalline structures with cage-like
%  cavities that allow movement and trapping of small solutes. The crystalline
%  frameworks are typically formed by networks of silicon and aluminum each 
%  attached to 4 oxygen atoms in a tetrahedral arrangement.~\cite{auerbach_handbook_2003}
%  One can replace the silicon and aluminum atoms via ion exchange in order to
%  control the size of the cavities and hence its molecular-seiving properties.~\cite{li_novel_2007}
%  A number of studies have tested the permeability and sodium salt rejection
%  of various zeolite membranes, however none have fully overcome the 
%  permeability-selectivity tradeoff.~\cite{pendergast_review_2011}
%%    \item Most are prone to defects in the crystalline structure.

@@

  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
  (LLC) membranes can be produced at moderate scale and may be capable of 
  performing highly selective separations~\cite{zhou_supported_2005,zhou_new_2007}. 
  LLCs are amphiphilic molecules that have the ability to self-assemble into
  porous nanostructures~\cite{smith_ordered_1997} that can be cross-linked 
  to create mechanically strong membrane films with periodic uniform-sized
  pores on the order of 1 nm in diameter~\cite{zhou_supported_2005}. 
  Since LLC polymer membranes have a very narrow pore size distribution, they 
  inherently exhibit high selectivity due to their molecular weight cut-off 
  (MWCO)~\cite{zhou_supported_2005}. Additionally, LLC monomers can be salts,
  and therefore lead to Donnan exclusion of ions at the membrane-feed solution 
  interface.\cite{donnan_theory_1995}
%    The membrane gains a net surface charge when counterions from
%  the head groups that line the pore walls escape into the feed solution in an
%  effort to balance the gradients of concentration and electric potential
%  \cite{donnan_theory_1995}.

  The feasibility of nanostructured LLC polymer membranes for selective separations
  has been demonstrated using LLC monomers that form the type 1 bicontinuous cubic
  (Q\textsubscript{I})~\cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
  and the inverted hexagonal (H\textsubscript{II}) 
  phases (see Figure~\ref{fig:structures}).~\cite{zhou_supported_2005} When separating organic solutes from NaCl, Q\textsubscript{I}-phase
  membrane filtration experiments have shown selectivity 2--3 times higher than
  commercial RO and 6--12 times higher than commercial NF membranes.~\cite{dischinger_application_2017}
  When separating a series of various sized dyes, an H\textsubscript{II}-phase 
  LLC membrane showed complete rejection of dyes bigger than 1.2 nm in size~\cite{zhou_supported_2005}.

@@

  \noindent There are four primary objectives of this PhD research which are 
  at various stages of completion.

  \begin{enumerate}

    \item Develop techniques to build and understand the nanoscopic structure
    of LLC membranes. (\textcolor{green!40!olive}{\textbf{Complete}})

    %MRS2: Objectives shouldn't include a description of what has and hasn't 
    %been done.  Then it's not an really just an objective anymore. I would 
    %suggest rephrasing these in terms of the intellectual objective, focusing
    %on the questions to be asked and hypotheses to be tested, and then talk 
    %in the next section about what has been done (or is to do).
    %BJC2: got it, rephrased first 2 objectives.

    A useful molecular-level model should incorporate a detailed picture 
    of the nanoscopic pore structure, which is crucial to understanding
    the role of monomer structure in solute transport and membrane design.
    Therefore, we must first create an atomistic model that is maximally 
    consistent with experimental structural data. It is also necessary to
    evaluate and justify the minimum effort required to build systems with
    alternate monomers while maintaining an experimentally-consistent 
    chemical environment.

%    I have created a maximally consistent structural model by comparing 
%    simulated X-ray diffraction (XRD) patterns, generated from MD trajectories,
%    to an experimental 2D wide angle X-ray scattering (WAXS) spectrum of a 
%    Col\textsubscript{h} phase LLC membrane. I have used this model as an 
%    example in order to 
%    %MRS2: I don't know that it's easy yet . . . 
%    %understand the ease with which 
%    demonstrate how 
%    we can apply our approach
%    to alternate monomers and other LC phases.

@@

    \item Determine solute-membrane interactions that give rise to
    transport mechanisms. (\textcolor{green!40!olive}{\textbf{Complete}})

    Using my most experimentally consistent configuration, I can place 
    small molecules within the H\textsubscript{II} nanopores and observe
    their behavior over simulation-accessible timescales. This objective 
    aims to organize observations of various solute behaviors into
    distinct mechanisms that can help guide membrane design based on 
    chemical functionality of both solutes and LLC monomers.

%    I observed the transport of a relatively large set of small polar solutes
%    placed within the H\textsubscript{II} phase membrane nanopores. I analyzed
%    the time series of each solute's position in addition to directly measuring
%    the physical interactions, such as hydrogen bonding and ion coordination, 
%    between solutes and LLC monomers.

    \item Create a stochastic model which can project long timescale 
    transport behavior. (\textcolor{blue}{\textbf{In Progress}})

@@

    \item Adapt the same analysis to the Q\textsubscript{I} phase. (\textcolor{blue}{\textbf{In Progress}})

@@

  \section{Progress to Date}\label{section:progress}

@@

  %BJC2: maybe a better way to present this
  \noindent My work fulfilling this objective is published in the Journal of Physical 
  Chemistry B: Coscia et al. \textit{J. Phys. Chem. B}, 123, 289-309 (2019).

  My first task was to develop a procedure for building and equilibrating 
  an atomistic LLC membrane system (see Figure~\ref{fig:assembly}). I chose to build
  a monoclinic unit cell consisting of four pores. Each pore is composed of monomer
  columns, where each column consists of 20 monomers stacked on top of each other
  so that the phenyl groups are coplanar with each other and the $xy$ plane. The
  columns are oriented so that the hydrophilic monomer head groups face towards
  the pore center. I did not add any water to the initial configuration because I
  compared the structure to experimental data for a system claimed to be
  synthesized with only neat monomer.

  %BJC2: removing unnecessary details
%  I equilibrated unit cells using a series
%  of simulations with head groups held in place by position restraints, gradually
%  reducing the force constant of the position restraints until the system
%  was completely unrestrained. I let the system equilibrate for 400 ns of simulation
%  time.

  %MRS2: above: less detail on what you did (for example, 400 ns of equilibration); 
  %focus on the point of the experiments (whatt hypothesis was tested) and what the 
  %results are.  committee members are going to be less interested in the details 
  %than the intellectual framework being used.
  %BJC2: implementing this idea throughout

@@

  I evaluated a number of different initial column architectures. I stacked 
  monomers in parallel displaced and sandwiched configurations, two possible
  $\pi$-$\pi$ stacking modes that might occur between monomer phenyl groups.
  ~\cite{sinnokrot_estimates_2002} I also varied the initial distance between
  stacked monomers, $d$. I chose $d$ values of 3.7~\AA, based on experimental
  WAXS measurements, as well as 5 \AA~as a test of its sensitivity.

@@

  \begin{wrapfigure}{L!}{0.5\textwidth}
    \centering
    \vspace{-0.5cm}
    \includegraphics[width=\linewidth]{p2p.pdf}
    \caption{Systems with 5 columns per pore have equilibrated pore spacings
            closest to the experimental value of 4.12 nm. The equilibrated 
            pore spacing of the model increases as the number of columns in
            each pore increases.}~\label{fig:p2p}
    \vspace{-1.25cm}
  \end{wrapfigure}

@@

  I further validated the structure of our molecular model by verifying 
  its consistency with five major reflections present in the experimental
  WAXS pattern. Using MD trajectories, we simulated X-ray diffraction (XRD)
  patterns that we could compare to the WAXS data by taking the appropriate
  cross-section of the time-averaged 3D structure factor. The five major 
  reflections and the structural features leading to them are summarized
  and described in the caption of Figure~\ref{fig:WAXS_comparison}. Note that
  none of the models simulated to this point could reproduce R-double.

  It is necessary to add a small amount of water to the model in order to 
  fully reproduce all features of the WAXS pattern (see Figure~\ref{fig:solvated_XRD}).
  I obtain the most experimentally consistent structure when I build systems
  in the parallel displaced configuration with 1 wt\% water added to the pores. 
  This is the only configuration that gives rise to the R-double feature without
  imposing some kind of position restraint. R-double appears because 
  vertically adjacent monomer head groups hydrogen bond with shared water molecules,
  causing them to be drawn closer together. When multiple pairing interactions
  occur in series along the same pore axis, the center of masses of the pairs 
  are spaced apart at twice the $\pi$-stacking distance. The necessity of water
  in my model suggests that the membrane synthesized by Feng et al.
  ~\cite{feng_scalable_2014,feng_thin_2016} was slightly hydrated due to water 
  molecules leached from surroundings by the hydroscopic monomers. Similar 
  suspicions have been voiced by experimentalists in unpublished communications.

  \begin{wrapfigure}{R!}{0.65\textwidth}
  	\centering
  	\vspace{-0.5cm}
    \begin{subfigure}{0.49\linewidth}
    	\includegraphics[width=\linewidth]{WAXS_annotated_words.pdf}
        \caption{Experiment}\label{fig:WAXS}
    \end{subfigure}
	\begin{subfigure}{0.49\linewidth}
        \includegraphics[width=\linewidth]{solvated_offset_rzplot_1.pdf}
        \caption{Simulation}\label{fig:solvated_XRD}   
	\end{subfigure}
    \caption{(a) 2D-WAXS gives details about repeating features on the order of
    angstroms. Explanations for each of the 5 major reflections present are
    as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack 3.7 \AA~apart. 
    (R-double) Monomer head groups associate into pairs by hydrogen bonding with
    a shared water molecule. R-double does not appear in dry systems. 
    (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer tails
    pack hexagonally. (R-pores) The pores are spaced 4.12 nm apart and pack 
    hexagonally. (b) We obtain a maximally consistent match between simulated
    XRD patterns and experimental WAXS data when we build systems in the 
    parallel displaced configuration with 1 wt \% water included in the pores.
    }\label{fig:WAXS_comparison}
    \vspace{-0.75cm}
 \end{wrapfigure}

  On the timescales that one can reasonably simulate, my model exhibits slow 
  dynamics. Consequently, there are very few uncorrelated frames in the 
  trajectories which leads to noise and sharpened reflections in the simulated
  XRD patterns. One can overcome this issue by combining the structure factors
  generated from an ensemble of simulated trajectories each produced
  from an ensemble of uncorrelated initial configurations. One can create 
  decorrelated initial configurations by randomly displacing monomer columns in
  the $z$-direction.

  Perhaps the most important conclusion from my structural work is that the 
  chemical composition of the pores is relatively insensitive to the initial 
  configuration. In Figure~\ref{fig:overlaid_densities}, I plot the radial 
  distribution function of various monomer components as a function of distance
  from the closest pore center. All are qualitatively similar meaning that a 
  solute placed in any of these systems should experience a similar chemical 
  environment. Although we will move forward with our most promising 
  configuration, this is an important finding since it implies that one does
  not need to apply the same level of rigor when screening new monomers.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  %BJC: probably change this legend to `d = x Angstroms` instead of 
  % disordered/ordered, since I don't have space to talk about ordered / disorderd configurations (requires 
  % nematic order parameter to give a complete justification of the names)
  \includegraphics[width=\textwidth]{regional_density_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.pdf}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.pdf}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.pdf}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  %MRS2: important consquence of all radian distribution functions being similar is that we should get useful transport details even if we didn't get the structure exactly right. 
  \caption{In all systems studied, the component radial distribution functions are similar.
      They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
          regions. The biggest differences are at r=0 where noise is higher due to
          decreased sampling. The center of the pore is not hollow, but contains sodium ions and
          head groups, even when the system is solvated. This architecture may impede transport in
          the real system in a chemically-dependent manner.
          The solvated system has a lower density of head groups near the
          pore center which is likely due to the swelling that is necessary in order to fit water
          molecules in the pore region.}~\label{fig:overlaid_densities}
  \vspace{-0.5cm}
  \end{figure}

@@

  \noindent A manuscript based on the work presented towards this objective is under 
  review for publication in the Journal of Physical Chemistry B.

  I added additional water to the most experimentally consistent structural
  model in order to create a higher water content H\textsubscript{II} phase
  model. Researchers have synthesized the H\textsubscript{II} phase using 
  the NaGA3C11 monomer with water contents ranging from 7 - 20 wt\%, with 
  close to 10 wt\% being the most common.~\cite{smith_ordered_1997,zhou_supported_2005} 
  However, Resel et al. stated that the system is likely fully hydrated at
  7 wt \% water with additional water trapped in defects between hexagonal
  mesophases.~\cite{resel_structural_2000} Consequently, we chose to build
  two systems with 5 and 10 wt\% water.

@@

  %MRS2: not great thesis statement.  Thesis statements should be trying to convince reader - this is just listing something you did. 
  %BJC2: tried again.
  I explored the influence of a solute's chemical functionality on its 
  transport properties within the H\textsubscript{II} nanopores using simulations
  of 20 different small polar solutes (see Table~\ref{fig:solute_table}).
  For each solute, I created a separate initial configuration and placed 6 
  solutes, equally spaced in $z$, in each nanopore. This gave a sufficient
  number of solute trajectories from which to generate statistics while 
  maintaining a low degree of interaction between solutes.

  % Unnecessary details
  % After a 5 ns equilibration, we allowed the solutes to simulate for
  % 1 microsecond.
